% ====================================================================
% IMPORTANT: This template REQUIRES XeLaTeX compiler!
% ====================================================================
% 
% In Overleaf: Menu -> Settings -> Compiler -> XeLaTeX
% In local TeX: Use 'xelatex main.tex' instead of 'pdflatex main.tex'
%
% ====================================================================
% Class Options
% ====================================================================
% - fontset: 'default' (open source) or 'commercial' (requires manual font files)
%   Example: fontset=default or fontset=commercial
%
% - pagefooter: boolean (default: true)
%   When enabled, shows a centered footer: "Name · current/total" (e.g., "Yuan Yuan · 2/3").
%   Set pagefooter=false to hide header/footer entirely.
\documentclass[fontset=default,pagefooter=false]{yuan2resume}

\name{Yuan Yuan}
\position{Ph.D. Candidate}
\phone{(+86) 1111-2222-3333}
\email{xxxx@xxxx.com}
\homepage{https://xxxx.github.io}

\begin{document}
\maketitle

\begin{cvtwocolumn}

\begin{cvsection}{Professional Experience}
  \cvpair{\textbf{ByteDance Ltd. }}{Shanghai, China}
  \cvpair{\textbf{Research Scientist}, AI for Science Group}{2022 -- \textit{Present}}
  \begin{cvitemize}
    \item Developed and implemented machine learning models for research projects, contributing to multiple publications
    \item Built scalable training infrastructure and optimized model performance using modern deep learning frameworks
    \item Collaborated with cross-functional teams to deploy research prototypes into production systems
  \end{cvitemize}
\end{cvsection}

\begin{cvsection}{Education}
  \cvpair{\textbf{University of California, Berkeley}}{Berkeley, CA}
  \cvpair{\textit{Ph.D. Candidate in Computer Science}}{Sept. 2020 -- \textit{Present}}
  \begin{cvitemize}
    \item Advisor: Prof. Alan Turing
    \item Research Area: Large Language Models, Efficient Inference, Distributed Systems.
    \item GPA: 3.96/4.0 (Rank: Top 1\%).
  \end{cvitemize}
  \cvpair{\textbf{Tsinghua University}}{Beijing, China}
  \cvpair{\textit{B.S. in Electrical Engineering and Computer Sciences (EECS)}}{Sept. 2016 -- June 2020}
  \begin{cvitemize}
    \item Graduated with High Distinction (Magna Cum Laude).
    \item Selected Coursework: Operating Systems (A+), Convex Optimization (A).
  \end{cvitemize}
\end{cvsection}

\begin{cvsection}{Publications}
  \vspace{-0.5\cvitemsep}
  \begin{cvnumlist}
    \item \textbf{Your Name}, Co-author. ``Xxxx Xxxx Xxxxxx Xx Xxx x Xxxx Xxxxx Xxxxx Xxxxxx.'' \textit{Proceedings of ACL}, 2023. (CCF-A)
    \item \textbf{Your Name}, First Author. ``Xxxx Xxx X Xxxx Xxxxx Xxxxxx Xxxxx Xxxxxx.'' \textit{Proceedings of NeurIPS}, 2022. (CCF-A)
    \item \textbf{Your Name}, Co-author. ``Xxx Xxxxxx Xxxxxx Xxxxx Xxxxxx Xxxxxx.'' \textit{Proceedings of EMNLP}, 2021. (CCF-B)
    \item \textbf{Your Name}, First Author. ``Xxxxxx Xxxxxx Xxxxxx Xxxxxx Xxxxxx.'' \textit{Proceedings of ICML}, 2020. (CCF-A)
  \end{cvnumlist}
\end{cvsection}

\begin{cvsection}{Skills}
  \textbf{Programming Languages}: {\CodeFont{Python}}, {\CodeFont{C++}}, {\CodeFont{Java}}, {\CodeFont{Rust}} \\
  \textbf{Machine Learning}: PyTorch, TensorFlow, Scikit-learn, XGBoost, Transformers \\
  \textbf{Big Data \& Infrastructure}: Apache Spark, Hadoop, Kubernetes, Docker, AWS, GCP, Distributed Systems \\
  \textbf{Languages}: English (Fluent), Chinese (Native), French (Basic)
\end{cvsection}
\vspace{\cvafterlist}

\begin{cvsection}{Awards\\and\\Honors}
  \cvpair{Outstanding Academic Achievement Award}{2022}
  \cvpair{Best Paper Award, Conference Name}{2021}
  \cvpair{Graduate Student Research Fellowship}{2020}
  \cvpair{Outstanding Student Leader Award, University Name}{2018, 2019, 2020}
\end{cvsection}

\end{cvtwocolumn}
\end{document}
